---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# criticalpath Package

<!-- badges: start -->
<!-- badges: end -->

criticalpath package is an object oriented implementation of the
Critical Path Method (CPM) in R with R6 library. CPM is a method used to estimate
the minimum project duration and  determine the amount of scheduling flexibility
on the logical network paths within the schedule model. The flexibility is in
terms of early start, early finish, late start, late finish, total float and
free float. Beside, it permits to quantify the complexity of network diagram
through the analysis of topological indicators. Finally, it permits to change
the activities duration to perform what-if scenario analysis.

With this package, you can calculate the following CPM parameters:

- Schedule duration
- Early start and finish date of each activity
- Late start and finish date of each activity
- Critical activities
- Critical path
- Total float and free float
- Gantt Matrix
- What-if scenario analysis
- Topological indicators


The aim of this package is to apply critical path method, for researchers to make experiments with CPM parameters.


## Installation

You can install the released version of criticalpath from [CRAN](https://CRAN.R-project.org) with:

``` {r}
#install.packages("criticalpath")
```

## Example

To create a schedule:

```{r example}
library(criticalpath)
# An empty schedule.
schedule <- Schedule$new()

# A schedule with activities and relations.
activities <- data.frame(
  id        = 1:17,
  name      = paste("a", as.character(1:17), sep=""),
  duration  = c(1,2,2,4,3,3,3,2,1,1,2,1,1,1,1,2,1)
)

relations <- data.frame(
  from = c(1, 1, 2, 2, 2, 3, 3, 3,  3,  4,  5,  6,
           7,  8,  9, 10, 11, 11, 12, 12, 13, 13, 14, 14, 15, 15),
  to   = c(2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 11, 11,
           12, 13, 14, 15, 16, 17, 16, 17, 16, 17, 16, 17, 16, 17)
)
schedule <- Schedule$new(activities, relations)
schedule$title <- "Project 1: Cost Information System"
schedule$reference <- "VANHOUCKE, Mario.
Integrated project management and control:
  first comes the theory, then the practice.
  Gent: Springer, 2014, p. 6"

```

What is the schedule duration?
```{r}
schedule$duration

```

Which activities are critical?
```{r}
schedule$activities$name[schedule$activities$critical]
```

What is the critical relations?
```{r}
schedule$relations[schedule$relations$critical, c(1,2)]
```

# More information

[CRAN - Package criticalpath](https://CRAN.R-project.org/package=criticalpath)

[criticalpath Page](https://rubensjoserosa.com/criticalpath)
