---
title: criticalpath - R Package Implementation of Critical Path Method
output: 
  rmarkdown::html_vignette:
    toc: TRUE
    toc_depth: 3
author:
  Rubens Jose Rosa, Marcos dos Santos, Thiago Marques
date: 2021-01-22
vignette: >
  %\VignetteIndexEntry{criticalpath Package Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r setup}
library(criticalpath)
```


# Introduction

## Critical Path Method

criticalpath package is an object oriented implementation of the
Critical Path Method (CPM) in R with R6 library. CPM is a method used to estimate
the minimum project duration and  determine the amount of scheduling flexibility
on the logical network paths within the schedule model. The flexibility is in
terms of early start, early finish, late start, late finish, total float and
free float. Beside, it permits to quantify the complexity of network diagram
through the analysis of topological indicators. Finally, it permits to change
the activities duration to perform what-if scenario analysis.

With this package, you can calculate the following CPM parameters:

- Schedule duration
- Early start and finish date of each activity
- Late start and finish date of each activity
- Critical activities
- Critical path
- Total float and free float
- Gantt Matrix
- What-if scenario analysis
- Topological indicators


The aim of this package is to apply critical path method, for the researcher to make experiments with CPM parameters.

# How to create a schedule

You have the following alternatives to create a schedule:

1. Create an empty schedule and add activities to i.
1. Create an empty schedule, add activities and relations to it.
1. Create an empty schedule and add activities at the same time that add relations to it.
1. Create an schedule from activities data frame and relations data frame.

Lets discuss each one.


## Add activities to a schedule

- `Schedule$add_activity(id, name, duration)` : 
adds an activity to a schedule.

- `Schedule$add_activities(activities)` : adds an activities data frame to a schedule.

Usage:

- Schedule$add_activity(id, name, duration)
- Schedule$add_activities(activities)

Parameters:

- `id` Activity id, an integer number that must be unique within a schedule.
It will be used to make relation between activities.
- `name` The name of activity. The default is an empty string.
- `duration` A number that represents the activity's duration.
It is integer number without time unit.
It must be equal or grater than zero. The default value is zero.
- `activities` Data frame with activities.
If it is not informed, the schedule will be created without any activity.
Its structure is defined in [schedule_from_data_frame]

```{r}
# Activities added one by one
schedule <- Schedule$new()
schedule$add_activity(1, "Task 1", 5)
schedule$add_activity(2, "Task 2", 6)
schedule$add_activity(3, "Task 3", 8)
schedule$add_activity(4, "Task 4", 6)
schedule$add_activity(5, "Task 5", 9)
schedule$add_activity(6, "Task 6", 3)
schedule$add_activity(7, "Task 7", 4)
schedule$duration
schedule$activities

# Activities add once for all
activities <- data.frame(
  id        = 1:17,
  name      = paste("a", as.character(1:17), sep=""),
  duration  = c(1,2,2,4,3,3,3,2,1,1,2,1,1,1,1,2,1)
)
schedule <- Schedule$new()
schedule$add_activities(activities)
schedule$duration
schedule$activities

```


## Add relations to a schedule

- Schedule$add_relation(from, to, type="FS", lag=0) : adds a relation to a schedule.

- Schedule$add_relations(relations) : adds a relations data frame to a schedule.

Usage

- Schedule$add_relation(from, to, type="FS", lag=0)
- Schedule$add_relations(relations)

Parameters: 

- `from` The id of predecessor activity. Must exist a activity with from id.
- `to` The id of successor activity. Must exist a activity with to.
- `type` Specifies the type of relation between activities. The default type is FS and its value may be: FS, FF, SS, SF, that means:

  - **FS:** Finish-Start relation.
Activity 'to' id can only start after the finish of activity 'from' id.

  - **FF:** Finish-Finish relation.
Activity 'to' id must finish together with activity 'from' id.

  - **SS:** Start-Start relation.
Activity 'to' id must start together with activity 'from' id.

  - **SF:** Start-Finish relation.
Activity 'to' id must finish when activity 'from' id starts.

- `lag` The time period between activities that the successor activity
'to' must be advanced after activity 'from' has been finished.
The value may be negative, in such case, the activity 'to' will be
anticipated 'lag' time periods.
It must be an integer, less than, equal or greater than zero.
If lag is not informed, it is assumed to be zero.
- `relations` Data frame with precedence relations between activities.
It is formed by predecessor activity e successor activity.
Its structure is defined in [schedule_from_data_frame].

```{r}
# First, create an empty schedule
schedule <- Schedule$new()
schedule$title <- "Project 3: Old Carriage House Renovation"
schedule$reference <-
  "VANHOUCKE, Mario. Integrated project management and control:
  first comes the theory, then the practice. Gent: Springer, 2014, p. 11"

# Second, add activities to it
schedule$add_activity(1, "a1" , 2)
schedule$add_activity(2, "a2" , 2)
schedule$add_activity(3, "a3" , 4)
schedule$add_activity(4, "a4" , 3)
schedule$add_activity(5, "a5" , 4)
schedule$add_activity(6, "a6" , 1)
schedule$add_activity(7, "a7" , 1)
schedule$add_activity(8, "a8" , 1)
schedule$add_activity(9, "a9" , 1)
schedule$add_activity(10, "a10", 1)
schedule$add_activity(11, "a11", 3)
schedule$add_activity(12, "a12", 2)
schedule$add_activity(13, "a13", 1)
schedule$add_activity(14, "a14", 1)
schedule$add_activity(15, "a15", 2)
schedule$add_activity(16, "a16", 1)
schedule$add_activity(17, "a17", 1)

# Finaly, add relations to it
schedule$add_relation( 1, 2)
schedule$add_relation( 2, 3)
schedule$add_relation( 3, 4)
schedule$add_relation( 4, 5)
schedule$add_relation( 5, 6)
schedule$add_relation( 6, 7)
schedule$add_relation( 6, 8)
schedule$add_relation( 6, 9)
schedule$add_relation( 7, 10)
schedule$add_relation( 8, 10)
schedule$add_relation( 9, 10)
schedule$add_relation( 10, 11)
schedule$add_relation( 10, 13)
schedule$add_relation( 11, 12)
schedule$add_relation( 12, 15)
schedule$add_relation( 13, 14)
schedule$add_relation( 14, 15)
schedule$add_relation( 15, 16)
schedule$add_relation( 16, 17)
schedule$duration
schedule$activities
schedule$relations
```


## Add activities and relations together to an schedule

Add an activity to a schedule in the same time that adds relations.

Usage

- Schedule$add_act_rel(id, name, duration, relations_id=c(), direction="succ")

Parameters:

- `id` Activity id, an integer number that
must be unique within a schedule.
It will be used to make relation between activities.
- `name` The name of activity.
- `duration` A number that represents the activity's duration.
It must be equal or grater than zero.
- `relations_id` A vector of ids such that will be linked with activity.
It may be a relations of successor or predecessors.
- `direction` Direction of relations_id: It may be "succ" or "pred".
  - **succ:** the relations_id vector will be the successor of the activity.
  - **pred:** the relations_id vector will be the predecessor of the activity.

```{r}
# Create a schedule
schedule <- Schedule$new()
schedule$title <- "Fictitious Project Example"
schedule$reference <- "VANHOUCKE, Mario. Measuring time:
  improving project performance using earned value management.
  Gent: Springer, 2009, p. 18"

# Add activities and relations to it.
schedule$add_act_rel(  1, "a1" , 0, c(2,3,4))
schedule$add_act_rel(  2, "a2" , 4, c(5))
schedule$add_act_rel(  3, "a3" , 9, c(10))
schedule$add_act_rel(  4, "a4" , 1, c(6))
schedule$add_act_rel(  5, "a5" , 4, c(9))
schedule$add_act_rel(  6, "a6" , 5, c(7))
schedule$add_act_rel(  7, "a7" , 1, c(8,11))
schedule$add_act_rel(  8, "a8" , 7, c(12))
schedule$add_act_rel(  9, "a9" , 8, c(12))
schedule$add_act_rel( 10, "a10", 3, c(12))
schedule$add_act_rel( 11, "a11", 3, c(12))
schedule$add_act_rel( 12, "a12", 0)
schedule$duration
schedule$activities
schedule$relations
```




## Create a schedule object from data frames

Make a schedule with activities and relations between activities.
The method `Schedule$new(activities, relations)`
creates an schedule object from two data frames,
one containing activities lists and the other the precedence relations
between activities.
After creation, it is applied the Critical Path Method (CPM).

It is possible to create a empty schedule, without any activity or relation
with the constructor `Schedule$new()`.
After that, it is possible to add activity with `add_activity`
and relation with `add_relation` methods.

Parameters:

- `activities` Data frame with activities.
If it is not informed, the schedule will be created without any activity.
Its structure is:
  - **id:** Activity id, an integer number that
must be unique within a schedule.
It will be used to make relation between activities.
  - **name:** The name of activity. The default is an empty string.
  - **duration:** A number that represents the activity's duration.
It is integer number without time unit.
It must be equal or grater than zero. The default value is zero.
- `relations` Data frame with precedence relations between activities.
If it is informed, the activities has to be informed too.
If is is not informed, the schedule will be created without any relation.
It is formed by predecessor activity e successor activity.
Its structure is:
  - **from:** The id of predecessor activity. Must exist a activity with from id.
  - **to:** The id of successor activity. Must exist a activity with to id.
  - **type:** Specifies the type of relation between activities.
The default type is FS and its value may be: FS, FF, SS, SF, that means:
      - **FS:** Finish-Start relation.
Activity 'to' id can only start after the finish of activity 'from' id.
      - **FF:** Finish-Finish relation.
Activity 'to' id must finish together with activity 'from' id.
      - **SS:** Start-Start relation.
Activity 'to' id must start together with activity 'from' id.
      - **SF:** Start-Finish relation.
Activity 'to' id must finish when activity 'from' id starts.
  - **lag:** The time period between activities that the successor activity
'to' must be advanced after activity 'from' has been finished.
The value may be negative, in such case, the activity 'to' will be
anticipated 'lag' time periods.
It must be an integer, less than, equal or greater than zero.
If it is not informed, it will be zero.

```{r}

# An empty schedule.
schedule <- Schedule$new()
schedule$duration
schedule$activities
schedule$relations

# A schedule with activities and relations.
activities <- data.frame(
  id        = 1:17,
  name      = paste("a", as.character(1:17), sep=""),
  duration  = c(1,2,2,4,3,3,3,2,1,1,2,1,1,1,1,2,1)
)

relations <- data.frame(
  from = c(1, 1, 2, 2, 2, 3, 3, 3,  3,  4,  5,  6,
           7,  8,  9, 10, 11, 11, 12, 12, 13, 13, 14, 14, 15, 15),
  to   = c(2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 11, 11,
           12, 13, 14, 15, 16, 17, 16, 17, 16, 17, 16, 17, 16, 17)
)
schedule <- Schedule$new(activities, relations)
schedule$title <- "Project 1: Cost Information System"
schedule$reference <- "VANHOUCKE, Mario.
Integrated project management and control:
  first comes the theory, then the practice.
  Gent: Springer, 2014, p. 6"
schedule$duration
schedule$activities
schedule$relations
```



# How to get schedule information

## Title, Reference and Schedule Duration
After a schedule is created, it is possible access several type of information:

- **title:**
A project title for identification. It depends on
user of the class. Its use are:

   - `Sechedule$title <- "A title"` : sets a title for a project.
   - `Sechedule$title` : gets the title of the project.

- **reference:**
A reference from project origin, for example, a book, a paper, a corporation,
or nothing.
   - `Sechedule$reference <- "A reference"` : sets a reference for a project.
   - `Sechedule$title` : gets the reference of the project.

- **duration:**
An integer value that indicate the project duration
calculated by CPM. Every time you include an activity or a relation
to a schedule, the duration is calculated. You can only read
the schedule duration.
   - `Sechedule$duration` : gets the duration of the project.

```{r}
# Create a schedule
schedule <- Schedule$new()
schedule$title <- "Fictitious Project Example"
schedule$reference <- "VANHOUCKE, Mario. Measuring time:
  improving project performance using earned value management.
  Gent: Springer, 2009, p. 18"

# Add activities and relations to it.
schedule$add_act_rel(  1, "a1" , 0, c(2,3,4))
schedule$add_act_rel(  2, "a2" , 4, c(5))
schedule$add_act_rel(  3, "a3" , 9, c(10))
schedule$add_act_rel(  4, "a4" , 1, c(6))
schedule$add_act_rel(  5, "a5" , 4, c(9))
schedule$add_act_rel(  6, "a6" , 5, c(7))
schedule$add_act_rel(  7, "a7" , 1, c(8,11))
schedule$add_act_rel(  8, "a8" , 7, c(12))
schedule$add_act_rel(  9, "a9" , 8, c(12))
schedule$add_act_rel( 10, "a10", 3, c(12))
schedule$add_act_rel( 11, "a11", 3, c(12))
schedule$add_act_rel( 12, "a12", 0)
schedule$title
schedule$reference
schedule$duration
```



# How to get activities properties


## Activity Properties

There several methods about activities that you can use to get
information about them. After you add activities to a schedule, you may
want to know how much activities has in a schedule or when each activity
is planned to start or to finish.
In this section, we will explain how you can find these information.

- **Has Any Activity:**
A logical value that indicate if the schedule
has any activity. A TRUE value means that the schedule has some
activity; a FALSE, means that the schedule is empty.
   - Usage: `Schedule$has_any_activity`

- **Number of Activities:**
Number of activities in a schedule as an integer value.
   - Usage: `Schedule$nr_activities`

- **Get activity:**
Gets an activity by id. It returns a data
frame with one line about activity. The structure of a data is
described in next topic.
   - Usage: `Schedule$get_activity(id)`

- **Activities:**
Return a data frame with all activities of a schedule
in a activity id order. This is the main information calculated by CPM.
The data frame is formed by following structure:
   - **id:** Activity id.
   - **name:** The name of activity.
   - **duration:** A number that represents the activity's duration.
   - **milestone:** A milestone is an activity with zero duration.
   This property indicates if a activity is a milestone or not:
   `TRUE` indicates it is a milestone; `FALSE` indicates it is not.
   - **critical:** A critical activity is one with total float minor or equal
   to zero. This property indicates if a activity is critical:
   `TRUE` indicates it is critical;
   `FALSE` indicates it is not critical.
   - **ES:** Early Start: is the earliest start period an activity can begin
   after its predecessors without violating precedence relation.
   - **EF:** Early Finish: is the early start plus activity duration.
   - **LS:** Late Start: is the late finish minus activity duration.
   - **LF:** Late Finish: is the latest finish an activity can finish
   before their successors without violating precedence relation.
   - **total_float:** It is the amount of period an activity can be
   delayed without violating the project duration. Its formula is:
   LS - ES or LF - EF.
   - **free_float:** It is the amount of period an activity can be
   delayed without violating the start time of the successors activities.
   - **progr_level:** Progressive level is the rank of activities counted
   from begin. The level of the activities that don't have predecessor is one;
   the level of the other activities, is one plus the maximal level of
   their predecessor.
   - **regr_level:** Regressive level is the rank of activities counted
   from the end. The level of the activities that don't have successor is the
   maximal progressive level; the level of the other activities,
   is one minus the minimal level of their successor.
   - **topo_float:** It is the difference between progressive level
    and regressive level.

   - Usage: `Schedule$activities`

   - Usage: `Schedule$get_activity(id)`

```{r}
# Create a schedule
schedule <- Schedule$new()
schedule$title <- "Fictitious Project Example"
schedule$reference <- "VANHOUCKE, Mario. Measuring time:
  improving project performance using earned value management.
  Gent: Springer, 2009, p. 18"

schedule$has_any_activity  # FALSE
schedule$nr_activities     # 0

# Add activities and relations to it.
schedule$add_act_rel(  1, "a1" , 0, c(2,3,4))
schedule$add_act_rel(  2, "a2" , 4, c(5))
schedule$add_act_rel(  3, "a3" , 9, c(10))
schedule$add_act_rel(  4, "a4" , 1, c(6))
schedule$add_act_rel(  5, "a5" , 4, c(9))
schedule$add_act_rel(  6, "a6" , 5, c(7))
schedule$add_act_rel(  7, "a7" , 1, c(8,11))
schedule$add_act_rel(  8, "a8" , 7, c(12))
schedule$add_act_rel(  9, "a9" , 8, c(12))
schedule$add_act_rel( 10, "a10", 3, c(12))
schedule$add_act_rel( 11, "a11", 3, c(12))
schedule$add_act_rel( 12, "a12", 0)

schedule$has_any_activity  # TRUE
schedule$nr_activities     # 12

schedule$get_activity(10)
schedule$activities
```


## Gantt Matrix

Create a matrix that represents a Gantt chart,
a matrix where "1" indicate that an activity is planned to be
in execution.

In this matrix, the rows represents activities,
Whereas the columns represents the activity execution period.
So, the number of columns is equal to project duration.

- `Schedule$gantt_matrix()` Return the Gantt matrix.

- `Schedule$xy_gantt_matrix(gantt=NULL)`
Transform a Gantt matrix in x, y coordinates and the weight one.
Each point greater than zero in a Gantt matrix becomes a x, y coordinate.

```{r}
activities <- data.frame(
  id        = c( 1,   2,   3,   4 ),
  name      = c("A", "B", "C", "D"),
  duration  = c( 2,   3,   1,   2 )
)
relations <- data.frame(
  from = c(1, 2, 4, 4),
  to   = c(3, 3, 1, 2)
)
schedule <- Schedule$new(activities, relations)
schedule$title <- "A project"
schedule$reference <- "From criticalpath"
gantt <- schedule$gantt_matrix()
gantt
# What is the effort by time period?
colSums(gantt) # 1 1 2 2 1 1
# What is the duration by activities?
rowSums(gantt) # 2 3 1 2
# what is the S curve
cumsum(colSums(gantt))
plot(cumsum(colSums(gantt)), type="l", lwd=3)
xyw <- schedule$xy_gantt_matrix()
xyw
plot(xyw[, 1:2])
```


# How to change activities duration

## Change Activities Duration

Change activities duration and calculate critical path.
This way is faster than creating a new schedule with new durations.
  new_durations A vector with new activities' duration.

**Attention:** The vector duration must be ordered by activity id.

- **Usage:** `Schedule$change_durations(new_durations)`

```{r}
activities <- data.frame(
  id        = 1:17,
  name      = paste("a", as.character(1:17), sep=""),
  duration  = c(1,1,3,2, 2,2,2,1, 4,5,3,3, 4,5,1,5,2)
)

relations <- data.frame(
  from = c(1, 2, 3, 3, 4, 5, 6, 7, 8,  8,  8,
    8,  8,  9, 10, 11, 12, 13, 13, 14, 14, 15, 15),
  to   = c(2, 3, 4, 6, 5, 8, 7, 8, 9, 10, 11,
   12, 13, 14, 14, 14, 14, 14, 15, 16, 17, 16, 17)
)

schedule <- Schedule$new(activities, relations)
schedule$title <- "Project 2: Patient Transport System"
schedule$reference <-
  "VANHOUCKE, Mario. Integrated project management and control:
  first comes the theory, then the practice. Gent: Springer, 2014, p. 9"
#Project duration
schedule$duration # 25
#Activities duration
schedule$activities$duration

new_durations <- c(1,2,5, 4,3, 2,1, 5, 3,5,5,3,4, 2,1, 2,4)
schedule$change_durations(new_durations)

#Project duration
schedule$duration # 31
#Activities duration
schedule$activities$duration

```


# How to get relations properties

## Relation Properties

There several methods about relations that you can use to get
information about them. After you add activities and relations
to a schedule, you may want to know how much relations has in a
schedule or which relations belong to critical path.
In this section, we will explain how you can find these information.

- **Has Any Relation:**
A logical value that indicates if the schedule
has any relation. A TRUE value means that the schedule has some
relation; a FALSE, means that the schedule does not have any relation.
   - Usage: `Schedule$has_any_relation`

- **Number of Relations:**
Number of relations in a schedule as an integer value.
   - Usage: `Schedule$nr_relations`

- **Relations:**
Return a data frame with all relations of a schedule
in topological order. This is the main information calculated by CPM.
The data frame is formed by following structure:
   - **from:** Predecessor activity id from a relation.
   - **to:** Successor activity id from a relation.
   - **type:** The type of relation between activities.
   Its value may be: FS, FF, SS, SF, as described in [schedule_from_data_frame]
   - **lag:** The time period between activity predecessor and
   activity successor activity
   - **critical:** A critical relation formed by two activity critical:
   predecessor and successor.
   `TRUE` indicates it is critical;
   `FALSE` indicates it is not critical.
   - **ord:** Indicates de order that the relation was added in the schedule.
   - **i_from:** It the index of predecessor activity in the
   activities data frame.
   - **i_to:** It the index of successor activity in the
   activities data frame.

   - Usage: `Schedule$relations`

```{r}
# Create a schedule
schedule <- Schedule$new()
schedule$title <- "Fictitious Project Example"
schedule$reference <- "VANHOUCKE, Mario. Measuring time:
  improving project performance using earned value management.
  Gent: Springer, 2009, p. 18"

schedule$has_any_relation  # FALSE
schedule$nr_relations      # 0

# Add activities and relations to it.
schedule$add_act_rel(  1, "a1" , 0, c(2,3,4))
schedule$add_act_rel(  2, "a2" , 4, c(5))
schedule$add_act_rel(  3, "a3" , 9, c(10))
schedule$add_act_rel(  4, "a4" , 1, c(6))
schedule$add_act_rel(  5, "a5" , 4, c(9))
schedule$add_act_rel(  6, "a6" , 5, c(7))
schedule$add_act_rel(  7, "a7" , 1, c(8,11))
schedule$add_act_rel(  8, "a8" , 7, c(12))
schedule$add_act_rel(  9, "a9" , 8, c(12))
schedule$add_act_rel( 10, "a10", 3, c(12))
schedule$add_act_rel( 11, "a11", 3, c(12))
schedule$add_act_rel( 12, "a12", 0)

schedule$has_any_relation  # TRUE
schedule$nr_relations      # 14

schedule$relations
```


## Successors and Predecessors

A schedule is structured by activities and each activity has
zero, one or more successors and predecessors. Besides, a relation
may be redundant.

- **All Successors:**
List all successors from an activity: direct and indirect successors.
   - Usage: `Schedule$all_successors(id, ign_to=NULL)`
     - **id** Activity id to be listed.
     - **ign_to** A relation to be ignored: id -> ign_to.
     Activities from this relation will be ignored.

- **All Predecessors:**
List all predecessors from an activity: direct or indirect predecessors.
   - Usage: `Schedule$all_predecessors(id, ign_from=NULL)`
     - **id** Activity id to be listed.
     - **ign_from** A relation to be ignored: ign_from -> id.
     Activities from this relation will be ignored.

- **Is Redundant:**
Verify if a relation between two activities is redundant.
A relation A->C is redundant if there are A->C, A->B, B->C relations.
It returns a logical `TRUE` if an arc is redundant;
`FALSE` if it is not.
   - Usage: `Schedule$is_redundant(id_from, id_to)`
     - **id_from** From activity id.
     - **id_to** To activity id.

```{r}
# Create a schedule
schedule <- Schedule$new()
schedule$title <- "Fictitious Project Example"
schedule$reference <- "VANHOUCKE, Mario. Measuring time:
  improving project performance using earned value management.
  Gent: Springer, 2009, p. 18"

# Add activities and relations to it.
schedule$add_act_rel(  2, "a2" , 4, c(5, 12))
schedule$add_act_rel(  3, "a3" , 9, c(10))
schedule$add_act_rel(  4, "a4" , 1, c(6))
schedule$add_act_rel(  5, "a5" , 4, c(9))
schedule$add_act_rel(  6, "a6" , 5, c(7))
schedule$add_act_rel(  7, "a7" , 1, c(8,11))
schedule$add_act_rel(  8, "a8" , 7, c(12))
schedule$add_act_rel(  9, "a9" , 8, c(12))
schedule$add_act_rel( 10, "a10", 3, c(12))
schedule$add_act_rel( 11, "a11", 3, c(12))
schedule$add_act_rel( 12, "a12", 0)

schedule$all_successors(2) # 5, 9, 12
schedule$all_successors(7) # 8, 11, 12
schedule$all_successors(10) # 12

schedule$all_predecessors(2) # nothing
schedule$all_predecessors(7) # 6, 4
schedule$all_predecessors(10) # 3

schedule$is_redundant(2, 5)  #FALSE
schedule$is_redundant(2, 12) #TRUE

```



# How to get topological properties

## Topological Indicators

Shows information about network structure. It may be of four type:

**SP Serial or Parallel:**
It shows the closeness of a network to a serial or parallel graph.
As the network becomes serial, the SP increase, until one,
when the network totally serial.
   - Usage: `Schedule$topoi_sp()`

**AD Activity Distribution:**
Measures the distribution of the activities over the levels.
If AD is approximately equal zero, each level has same numbers of activities.
Otherwise, if AD is equal one, the quantity of each level is not
uniformly distributed.
   - Usage: `Schedule$topoi_ad()`

**LA Length of Arcs:**
Measures the presence of long arcs based on the difference between
the progressive level of the end activity and the start node
of each relation.
If LA is approximately equal zero, the progressive level between
activities are as far as possible.
Otherwise, if LA is equal one, the relation distance are one.
   - Usage: `Schedule$topoi_la()`

**TF Topological Float Indicator:**
Measures the topological float of each activity.
If TF = 0, there is no float between activities.
If TF = 1, there is float between activities
and they be shift without affecting other activities.
   - Usage: `Schedule$topoi_tf()`

```{r}
# Create a schedule
schedule <- Schedule$new()
schedule$title <- "Fictitious Project Example"
schedule$reference <- "VANHOUCKE, Mario. Measuring time:
  improving project performance using earned value management.
  Gent: Springer, 2009, p. 18"

# Add activities and relations to it.
schedule$add_act_rel(  1, "a1" , 0, c(2,3,4))
schedule$add_act_rel(  2, "a2" , 4, c(5))
schedule$add_act_rel(  3, "a3" , 9, c(10))
schedule$add_act_rel(  4, "a4" , 1, c(6))
schedule$add_act_rel(  5, "a5" , 4, c(9))
schedule$add_act_rel(  6, "a6" , 5, c(7))
schedule$add_act_rel(  7, "a7" , 1, c(8,11))
schedule$add_act_rel(  8, "a8" , 7, c(12))
schedule$add_act_rel(  9, "a9" , 8, c(12))
schedule$add_act_rel( 10, "a10", 3, c(12))
schedule$add_act_rel( 11, "a11", 3, c(12))
schedule$add_act_rel( 12, "a12", 0)

schedule$topoi_sp()
schedule$topoi_ad()
schedule$topoi_la()
schedule$topoi_tf()
```



# References

Csardi, G. & Nepusz, T. (2005).
The Igraph Software Package for Complex Network Research.
**InterJournal**. Complex Systems. 1695.

Project Management Institute (2017)
**A Guide to the Project Management Body of Knowledge (PMBOK Guide)**.
Sixth Edition.

Project Management Institute (2017)
**PMI Lexicon of Project Management Terms:** Version 3.2.

Vanhoucke, M. (2009) **Measuring Time**:
Improving Project Performance Using Earned Value Management.
Springer-Verlag US.

Vanhoucke, M. (2013) **Project Management with Dynamic Scheduling**:
Baseline Scheduling, Risk Analysis and Project Control.
Springer-Verlag Berlin Heidelberg.

Vanhoucke, M. (2014) **Integrated Project Management and Control**:
First Comes the Theory, then the Practice.
Springer International Publishing Switzerland.
